---
output:
  word_document: default
  html_document: default
---



-	**help.start():** Start the hypertext (currently HTML) version of R's online documentation.
-	**help(command)/??command/help.search(command):** display the help related to a specific command.
-	**demo():** is a user-friendly interface to running some demonstrations of R scripts.
-	**library(help=package):** list functions and datasets in a package.
-	**getwd():**  print the current working directory.
-	**ls():** list the objects in the current workspace.
-	**setwd(mydirectory):** change working directory to mydirectory.
-	**options():** view current option settings.
-	**options(digits=3):** number of digits to print on output.
-	**history():** display last 25 commands.
-	**history(max.show=Inf):** display all previous commands.
-	**savehistory(file="myfile"):** save the history (default file is a ".Rhistory" file).
- **loadhistory(file="myfile"):** recall your command history.
- **save.image():** save the workspace to the file “.RData” in the working directory.
-	**save(object list,file="myfile.RData"):** save specific objects to a file.
-	**load("myfile.RData"):** load specific object from a file.
-	**q():** quit R. You will be prompted to save the workspace.
-	**library(package):** loads a library specific to a project.
-	**install.package(package):** download and install packages from CRAN-like repositories or from local files.
-	**rm(object1, object2…):** remove objects.



```{r}

n<-10
n

```


```{r}

n+5

```



```{r}

x<-4
y<-3

```


```{r}

x + y

```



```{r}

x - y

```


```{r}

x * y

```



```{r}

x / y

```



```{r}

x ** y

```



```{r}

x * pi

```



```{r}

exp(y)

```



```{r}

sign(y)

```



```{r}

max(x,y)

```



```{r}

min(x,y)

```


```{r}

factorial(y)

```



```{r}

sqrt(y)

```



```{r}

z <- x + y
z

```




```{r}

x > y

x + y != 8

```



```{r}

a<-c(1,3,5,8)
a

```



```{r}

y <- c(1,3)
class(y)

```



```{r}

y <- c(1,5,1)
y + 3

```



```{r}

c(1:10)

```



```{r}

seq(1, 5, by=0.1)

seq(1, 5, length.out=22)

```



```{r}

rep(3,20)

```



```{r}

x <- c(9,8,1,5)

```



```{r}

x[-3]

```



```{r}

x[1:2]

```


```{r}

x[x>0 & x<4]

```



```{r}

x[c(TRUE, FALSE, FALSE, TRUE)]

```


```{r}

sum(x)

```



```{r}

prod(x)

```




```{r}

length(x)

```



```{r}

x

x[1]<-22

x

```


```{r}

r<-c(1,4,7,9,8,1)
r<-factor(r)
r

```



```{r}

levels(r)

```



```{r}

factor(r, exclude=4)

```



```{r}

a<- c(1,2,7,7,1,2,2,7,1,7)
a<- factor(a, levels=c(1,2,7), ordered=TRUE)
a

```



```{r}

c<-"This is our first string"
c

class(c)

```



```{r}

nchar(c) 

```



```{r}

substring(c,4) 

```



```{r}

substring(c,1,4) 

```




```{r}

strsplit(c, " ") 

```



```{r}

grep("our", c) 

grep("book", c)

```



```{r}

regexpr("our", c) 

```



```{r}

tolower(c)

```


```{r}

toupper(c)

```


```{r}

sub("our", "my", c) 

```



```{r}

gsub("our", "my", c) 

```


```{r}

paste(c,"My book",sep=" : ")

```



```{r}

m<-matrix(c(1,2,3,4,5,6), nrow=2, ncol=3)
m

```



```{r}

m<-matrix(c(1,2,3,4,5,6), nrow=2, ncol=3,byrow=TRUE)
m

```

 

```{r}

m<-matrix(c(1,2,3,4,5,6), nrow=2, ncol=3,byrow=TRUE,dimnames=list(c('Obs1', 'Obs2'), c('col1', 'Col2','Col3')))
m

```



```{r}

rbind(1:3,4:6,10:12)

cbind(1:3,4:6,10:12)
 
m<-array(c(1,2,3,4,5,6), dim=c(2,3))
m

```



```{r}

m<-array(c(1,2,3,4,5,6), dim=c(2,3))
m

```

```{r}

m[1,2]

```


```{r}

m[2,2]

```



```{r}

m[2,]

```



```{r}

m[,1]

```



```{r}

m<-matrix(c(1,2,3,4,5,6,7,8,9), nrow=3, ncol=3)
m

diag(m)

```



```{r}

dim(m)

```



```{r}

colSums(m)

```



```{r}

rowSums(m)

```



```{r}

t(m)

```



```{r}

det(m)

```



```{r}

eigen(m)

```



```{r}

x<- list(1:4,"book",TRUE, 1+4i)
x

```


```{r}

x[[1]]

```



```{r}

x[[1]][2:4]

```


```{r}

a <- c(1, 3, 5) 
b <- c("red", "yellow", "blue") 
c <- c(TRUE, FALSE, TRUE) 
df <- data.frame(a, b, c)  
df
```




```{r}

df[2,1]

```



```{r}

df[,"a"]

```



```{r}

data(iris)

```




```{r}

ncol(iris)

```



```{r}

nrow(iris)

```


```{r}

head(iris,10)

```


```{r}

tail(iris,5)

```


```{r}

str(iris)

```



```{r eval = FALSE}

install.packages("foreign")

library(foreign)

```



```{r eval = FALSE}

install.packages("Hmisc")

library(Hmisc)

```



```{r eval = FALSE}

mydata<-read.table("c:/mydata.csv", header=TRUE,sep=",", row.names="id")

```



```{r eval = FALSE}

library(xlsx)
mydata<-read.xlsx("c:/myexcel.xlsx", 1)

```



```{r eval = FALSE}

mydata<-read.xlsx("c:/myexcel.xlsx", sheetName= "mysheet")

```



```{r eval = FALSE}

library(foreign)
mydata<-read.systat("c:/mydata.dta")

```


```{r eval = FALSE}

library(Hmisc)
mydata<-spss.get("c:/mydata.por", use.value.labels=TRUE)


```


```{r eval = FALSE}

library(Hmisc)
mydata<-sasxport.get("c:/mydata.xpt")

```


```{r eval = FALSE}

library(foreign)
mydata<-read.dta("c:/mydata.dta")

```


```{r eval = FALSE}

write.table(mydata, "c:/mydata.txt", sep="\t") 

```


```{r eval = FALSE}

library(xlsx)
write.xlsx(mydata, "c:/mydata.xlsx")

```


```{r eval = FALSE}

library(foreign)
write.foreign(mydata, "c:/mydata.txt", "c:/mydata.sps",   package="SPSS") 

```


```{r eval = FALSE}

library(foreign)
write.foreign(mydata, "c:/mydata.txt", "c:/mydata.sas",   package="SAS")

```


```{r eval = FALSE}

library(foreign)
write.dta(mydata, "c:/mydata.dta")

```


```{r}

squaredNum<-function(number){
  a<-number^2
  return(a)
}

```


```{r}

squaredNum(425)

```



```{r}

x<-4
y<-3

```

```{r}

if (x >3) {
 y <- 10
} else {
 y<- 0
}

```



```{r}

print(y)

```



```{r}

for (i in 1:10){
 print(i)
}

```


```{r}

x<- matrix(1:6,2,3)

for (i in seq_len(nrow(x))){
  for (j in seq_len(ncol(x))){
    print(x[i,j])}
}

```



```{r}

x <- 1

while (x >= 1 & x < 20) {
  print(x)
  x = x+1
  }

```



```{r}

x <- 1

repeat {
  print(x)
  x = x+1
  if (x == 6){
    break 
    }
  }

```



```{r}

for (i in 1:15){
     if (i <= 5){
     next
     } else { print(i)
 } }

```





 

